Investigation of thermal reactionomes reveals stress tolerance vs. resistance in

### 2014-08-27 doc/ApTranscriptome_manuscript.Rmd
fixed Rmd to compile

---
title: Investigation of thermal reactionomes reveals stress tolerance vs. resistance in
  warm and cold-climate ant species \\
author: \centering{John Stanton-Geddes \textsuperscript{1}, Andrew Nguyen \textsuperscript{1},
  James Vincent \textsuperscript{2}, Mahesh Vangala \textsuperscript{2}, Robert R.
  Dunn \textsuperscript{3}, Nathan J. Sanders \textsuperscript{4}, Nicholas J. Gotelli
  \textsuperscript{1}, Sara Helms Cahan \textsuperscript{1} \\ \vspace{5 mm} \textsuperscript{1}
  Department of Biology, University of Vermont \\ \textsuperscript{2} Vermont Genetics
  Network, University of Vermont \\ \textsuperscript{3} Department of Biological Sciences,
  North Carolina State University \\ \textsuperscript{4} Center for Macroecology,
  Evolution and Climate, University of Copenhagen}
csl: ecology.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    toc_depth: 2
  html_document: null
  word_document: default
includes: header.tex
bibliography: ApTranscriptome.bib
---

@@

The combined *Aphaenogaster* transcriptome assembly contained 99,861 transcripts, hereafter referred to as genes.  Of these, we identified `r prettyNum(sum(sigtable[sigtable$Coefficient %in% c("Temperature", "Temperature:Colony"), "Number.significant"]), big.mark = ",", scientific = FALSE)` genes with expression patterns that were thermally-responsive at 5% False Discovery Rate. Thus, at a minimum `r round(9100/99861, 2)*100`% of genes are thermally-responsive. However, the closest related ant species with sequenced genomes have only about 17,000 genes [@gadau2012]. Assuming that the number of genes is similar for these two *Aphaenogaster* species, this suggests that up to 50% of the genome (9,100 / 17,000) could be thermally-responsive.

@@

```{r max_exp_PDF, eval = FALSE,aniopts= echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Probability density function of the temperature of maximum expression for all thermally-responsive genes in each species."}
# reshape data
Ap.df$Species <- ifelse(Ap.df$colony == "ApVT", "A. picea", "A. carolinensis")

>>>>

---
title: Investigation of thermal reactionomes reveals stress tolerance vs. resistance in
  warm and cold-climate ant species
author: \centering{John Stanton-Geddes \textsuperscript{1}, Andrew Nguyen \textsuperscript{1},
  James Vincent \textsuperscript{2}, Mahesh Vangala \textsuperscript{2}, Robert R.
  Dunn \textsuperscript{3}, Nathan J. Sanders \textsuperscript{4}, Nicholas J. Gotelli
  \textsuperscript{1}, Sara Helms Cahan \textsuperscript{1} \\ \vspace{5 mm} \textsuperscript{1}
  Department of Biology, University of Vermont \\ \textsuperscript{2} Vermont Genetics
  Network, University of Vermont \\ \textsuperscript{3} Department of Biological Sciences,
  North Carolina State University \\ \textsuperscript{4} Center for Macroecology,
  Evolution and Climate, University of Copenhagen}
csl: ecology.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    toc_depth: 2
  html_document: null
  word_document: default
includes: header.tex
bibliography: ApTranscriptome.bib
---

@@

The combined *Aphaenogaster* transcriptome assembly contained 99,861 transcripts.  Of these, we identified `r prettyNum(sum(sigtable[sigtable$Coefficient %in% c("Temperature", "Temperature:Colony"), "Number.significant"]), big.mark = ",", scientific = FALSE)` transcripts genes with expression patterns that were thermally-responsive at 5% False Discovery Rate. Thus, at a minimum `r round(9100/99861, 2)*100`% of genes are thermally-responsive. However, the closest related ant species with sequenced genomes have only about 17,000 genes [@gadau2012]. Assuming that the number of genes is similar for these two *Aphaenogaster* species, this suggests that up to 50% of the genome (9,100 / 17,000) could be thermally-responsive.

@@

```{r max_exp_PDF, eval = FALSE, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Probability density function of the temperature of maximum expression for all thermally-responsive genes in each species."}
# reshape data
Ap.df$Species <- ifelse(Ap.df$colony == "ApVT", "A. picea", "A. carolinensis")
